Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*

### 2014-03-26 paper/tex/Paper.tex
lkdsj

\author{
Joel Venzke, Paxten Johnson, Rachel Davis, John Emmons, Katherine Roth,\\ David Mascharka, Leah Robison, Timothy Urness and Adina Kilpatrick\\
Department of Mathematics and Computer Science\\
Drake University\\
Des Moines, IA\\
email %TODO
}
\date{}

>>>>

\author{
Joel Venzke, Paxten Johnson, Rachel Davis, John Emmons, Katherine Roth,\\ David Mascharka, Leah Robison, Timothy Urness and Adina Kilpatrick\\
Department of Mathematics and Computer Science\\
Drake University\\
Des Moines, IA\\
email % TODO
}
\date{}
